Developing a preprint culture in biology

### 2012-09-28 ms.tex
add license discussion

@@

Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
that allows scientists to submit any research output: manuscript, figures,
datasets, videos, theses, presentations, and so on. There are no rules to limit
what constitutes a research output and, unlike arXiv, there is no endorser
system. All figshare content has a unique digital object identifier (DOI) like
any journal article, thus offering a permanent and stable link to the content.
A flexible tag system is used to classify the content. All content can
be commented and is licensed under the Creative Commons (CC-BY) license, except
datasets which are published under CC0.

>>>>

% To review: 
To submit to arXiv, the authors must either have their work available under an
open license or grant arXiv a non-exclusive and irrevocable license to
distribute the article. In either case, arXiv does not require copyright
transfer and only requires the rights to distribute submitted articles in
perpetuity. Thus, submitting to arXiv does not in itself prevent the authors
from transferring their rights to a publisher, which is why most publishers
tolerate arXiv, even though they ask the authors to transfer their right to them
upon acceptance of the article.

@@

Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
that allows scientists to submit any research output: manuscript, figures,
datasets, videos, theses, presentations, and so on. There are no rules to limit
what constitutes a research output and, unlike arXiv, there is no endorser
system. All figshare content has a unique digital object identifier (DOI) like
any journal article, thus offering a permanent and stable link to the content.
A flexible tag system is used to classify each item. All content can be
commented and is licensed under the Creative Commons (CC-BY) license, except
datasets which are published under CC0.
